Effectful Semantics for Substructural SSA

### 2023-11-13 pldi24/paper.tex
Tap

\TODO{in particular, these induce a substructural effectful category...}

\subsection{Heaps and Separation Logic}

@@

We'll start by considering the category \(\ms{HRel}\), which we will take to have morphisms of the form \(A \to \ms{Heap} \to \mc{P}^+(A \times \ms{Heap} \times \ms{Bytes}^* + \ms{Bytes}^{\leq \omega})\), which is the result of applying the state-transformer monad with state \(\ms{Heap}\) to the trace monad with the monoid of lists of bytestrings described in the previous section.

\TODO{say something better than "bytestrings"}

\TODO{Use name \ms{Traces}}

@@

Given a set \(A\), we can define a predicate \(\varphi\) on \(A\), \(\mb{Heap}\) pairs to have the following type:
\TODO{this}
\TODO{Objects \((A, \varphi)\), \((B, \psi)\)}
\TODO{arrows}
\TODO{note on magic wand}
\TODO{Tensor product and separating conjunction}
\TODO{Coproduct, Elgot structure inherited from base category}
\TODO{sliding w/ properly restricted equality}
\TODO{equality vs \cite{mellies-ftrs}}
\TODO{potential solutions}

\TODO{so, it's a substructural effectful category mmkay}
\TODO{central = no printing}
\TODO{linear objects iff non duplicable}
\TODO{relevant morphisms iff deterministic}
\TODO{affine morphisms always (if no heap effects?)}

>>>>

\subsection{Heaps, Printing, and Separation Logic}

As a concrete example, we can now introduce the \textbf{printing monad}, which is simply defined as \(\ms{Print}\;A \equiv \ms{Traces}\;\Sigma\), where \(\Sigma: (\ms{Bytes}^*)^\omega \to \ms{Bytes}^{\leq \omega}\) denotes concatenation of lists of bytestrings.

\TODO{substructural effectful category}

\TODO{heap via \(\ms{StateT}\), lifting of central/relevant/affine submonads}

\TODO{segue to separation logic}

@@

@@

Given a set \(A\), we can define a predicate \(\varphi\) on \(A\), \(\mb{Heap}\) pairs to have the following type:
\TODO{this}
\TODO{Objects \((A, \varphi)\), \((B, \psi)\)}
\TODO{arrows}
\TODO{note on magic wand}
\TODO{Tensor product and separating conjunction}
\TODO{Coproduct, Elgot structure inherited from base category}

\TODO{so, it's a substructural effectful category mmkay}
\TODO{central = no printing, no heap}
\TODO{linear objects iff non duplicable}
\TODO{relevant morphisms iff deterministic}
\TODO{affine morphisms always (if no heap effects?)}

\TODO{equality vs \cite{mellies-ftrs}}
\TODO{sliding w/ properly restricted equality}
\TODO{\(\implies\) central = no printing, heap allowed}
